Paradigms in Physics 2.0

### 2018-09-27 proposal.tex
initial proposal

\documentclass[aps,prstper,reprint]{revtex4-1}   
\usepackage{graphicx}
\usepackage{hyperref}  
\hypersetup{colorlinks=true,urlcolor=blue,citecolor=blue,linkcolor=blue}   
\urlstyle{same}
\pagestyle{empty}		% page numbers added later, when compiling the whole proceedings

\newcommand\corinnesays[1]{\textcolor{red}{[\sc CAM: {\em#1}]}}
\newcommand\davidsays[1]{\textcolor{blue}{[\sc DR: {\em#1}]}}
\renewcommand\davidsays[1]{}

@@

\title{Paradigms in Physics 2.0}
\author{David Roundy}
\author{Elizabeth Gire}
\author{Ethan Minot}
\author{Emily van Zee}
\affiliation{Department of Physics, Oregon State University, Corvallis, Oregon, 97331}
\author{Corinne A. Manogue}
\affiliation{Department of Physics, Oregon State University, Corvallis, Oregon, 97331}

@@

\section{Theoretical basis for the work}
The framework for this study was adapted from studies of
organizational decision-making\cite{beach2006leadership}. Leaders in
an organization ``must work with others within the organization (1) to
understand the organization's internal and external environments, (2)
to understand the organization's culture, (3) to create a vision of a
desirable future and obtain buy-in, (4) to design a plan that moves
the organization toward the envisioned future, (5) to integrate the
various units in implementation of the plan and to monitor progress
and (6) to institutionalize achieved changes and make continuous
change an integral part of the organization's culture'' (Beach ,
p. ix).  \cite{beach2006leadership}
\section{Research questions}
\begin{itemize}
\item What was the educational reform context within which the faculty
  initiated revising the upper-level physics curriculum?
\item What was the culture of the department at that time? In
  particular, what were the participants' beliefs about teaching and
  learning?
\item What motivated making changes and how did the faculty form a
  coherent vision for the new program?
\item How did the faculty develop and communicate plans for this new
  curriculum?
\item How have they changed instruction based upon the proposals that
  the faculty approved with an unanimous vote?
\end{itemize}
\section{Research methods}
We performed interviews of faculty before, during and after the
Paradigms 2.0 process, gave surveys to students and faculty, and had
an observer take notes during all Paradigms 2.0 meetings.

>>>>

\documentclass[aps,prstper,reprint]{revtex4-1}
\usepackage{graphicx}
\usepackage{hyperref}
\hypersetup{colorlinks=true,urlcolor=blue,citecolor=blue,linkcolor=blue}
\urlstyle{same}

\newcommand\corinnesays[1]{\textcolor{red}{[\sc CAM: {\em#1}]}}
\newcommand\davidsays[1]{\textcolor{blue}{[\sc DR: {\em#1}]}}

@@

\title{Paradigms in Physics 2.0}
\author{David Roundy}
\email{roundyd@physics.oregonstate.edu}
\author{Elizabeth Gire}
\author{Ethan Minot}
\author{Emily van Zee}
\affiliation{Department of Physics, Oregon State University, Corvallis, Oregon, 97331}
\author{Corinne A. Manogue}
\affiliation{Department of Physics, Oregon State University, Corvallis, Oregon, 97331}

@@

This paper will describe both the process of the reform and its
outcome, but the emphasis of the paper and the research aspect of it
will be on the process by which we developed the changes and arrived
at consensus.  This is paper is thus on the coarse-grained picture of
how one department acheived a broad-scale reform of its curriculum,
which we expect will serve as a valuable balance to the more
fine-grained view that is needed for classroom activities.  In
addition to the Paradigms 2.0 reform, we will briefly introduce the
original effort that began in 1996, and give a bit more detail on how
that reform was maintained and refined during the intervening decades.

This story of how we achieved a dramatic curriculum change will be
useful for other departments considering a reform of their curriculum.
Few departments embark on such an endeavor, and publishing a blueprint
for how we managed this will be helpful for others seeking to reform
their curriculum.

\paragraph*{Theoretical basis for the work}
The framework for this {\bf empirical study} was adapted from studies
of organizational decision-making\cite{beach2006leadership}.  Like the
process that led to Paradigms 1.0, the Paradigms 2.0 process is a
``shared vision'' type of change\cite{henderson2010}. Changes to the
course structures of the physics curriculum emerged from discussions
among the members of the department. The Paradigms~2.0 process began
in the Winter of 2016, after the faculty agreed to the process during
the previous year.

\paragraph*{Research questions}
\begin{itemize}
\item What was the educational reform context within which the faculty
  initiated revising the upper-level physics curriculum?
\item What was the culture of the department at that time? In
  particular, what were the participants' beliefs about teaching and
  learning?
\item What motivated making changes and how did the faculty form a
  coherent vision for the new program?
\item How did the faculty develop and communicate plans for this new
  curriculum?
\item How have they changed instruction based upon the proposals that
  the faculty approved with an unanimous vote?
\end{itemize}
\paragraph*{Research methods}
We performed interviews of faculty before, during and after the
Paradigms 2.0 process, gave surveys to students and faculty, and had
an observer take notes during all Paradigms 2.0 meetings.
